\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Bibliography}
\begin{thebibliography}{99}

\bibitem{aut_wiki_cat_8}  
Julian Szymański, Marcin Roman, Grzegorz Borczuch, Radosław Szulgo, "AUTOMATYCZNA KATEGORYZACJA ARTYKUŁÓW WIKIPEDII", Politechnika Gdańska, Wydział Elektroniki Telekomunikacji i Informatyki, Katedra, Architektury Systemów Komputerowych, ZESZYTY NAUKOWE WYDZIAŁU ETI POLITECHNIKI GDAŃSKIEJ, nr 8/2010

\bibitem{wiki_art_num}
Number of articles in English Wikipedia, https://en.wikipedia.org/wiki/Wikipedia:Size\_of\_Wikipedia, accessed on 09.07.2015

\bibitem{digitalization}
Lovrek, Ignac, Howlett, RobertJ, Jain, LakhmiC, "Comparing Document Classification Schemes Using K-Means Clustering"

\bibitem{naive-bayesian}
Deshpande, V.P.; Erbacher, R.F.; Harris, C., "An Evaluation of Naive Bayesian Anti-Spam Filtering Techniques," in Information Assurance and Security Workshop, 2007. IAW '07. IEEE SMC , vol., no., pp.333-340, 20-22 June 2007

\bibitem{bayesian-history}
Roger C. Barr, Loren W. Nolte, and Andrew E. Pollard, "Bayesian Quantitative Electrophysiology and Its Multiple Applications in Bioengineering". IEEE Rev Biomed Eng. 2010; 3: 155–168.
doi:  10.1109/RBME.2010.2089375


\bibitem{data-mining}
Hastie, Trevor; Tibshirani, Robert; Friedman, Jerome (2009). "The Elements of Statistical Learning: Data Mining, Inference, and Prediction". http://statweb.stanford.edu/~tibs/ElemStatLearn/ access 23.08.2015

\bibitem{data-mining-kdd}
Usama Fayyad, Gregory Piatetsky-Shapiro, Padhraic Smyth, "From Data Mining to Knowledge Discovery in Databases", http://www.kdnuggets.com/gpspubs/aimag-kdd-overview-1996-Fayyad.pdf access 19.08.2015

\bibitem{fe_signal_processing}
TBD

\bibitem{lookup-stem}
Sharifloo, A. A. and Shamsfard, M. 2008. "A Bottom up Approach to Persian Stemming", in the Proceedings of the Third International Joint Conference on Natural Language Processing. Hyderabad, India.

\bibitem{suffix-stripping}
M.F.Porter, "An algorithm for suffix stripping", Program 14, no. 3, pp 130-137, July 1980.

\bibitem{lemma}
Karl Ingason, Sigrún Helgadóttir, Hrafn Loftsson, Eiríkur Rögnvaldsson, "A Mixed Method Lemmatization Algorithm
Using a Hierarchy of Linguistic Identities (HOLI)", A. Ranta, B. Nordström (Eds.): GoTAL 2008, LNAI 5221, pp. 205–216, 2008.
c Springer-Verlag Berlin Heidelberg 2008

\bibitem{term-frequency}
Rajaraman, A.; Ullman, J. D. (2011). "Data Mining". Mining of Massive Datasets (PDF). pp. 1–17. doi:10.1017/CBO9781139058452.002. ISBN 9781139058452.

\bibitem{association-rules}
Piatetsky-Shapiro, Gregory (1991), Frawley, William J, "Discovery, analysis and presentation of strong rules", Knowledge Discovery in Databases, AAAI/MIT Press, Cambridge, MA.

\bibitem{fp-growth}
Florian Verhein, "Frequent Pattern Growth (FP-growth) algorithm", School of Information technologies, The University of Sydney, Australia, June 2008

\bibitem{knn}
Bhavani Thuraisingham,Latifur Khan,Mamoun Awad,Lei Wang, "Design and Implementation of Data Mining Tools", CRC Press, 18.06.2009

\bibitem{knn2}
Saravanan Thirumuruganathan, "A Detailed Introduction to K-Nearest Neighbor (KNN) Algorithm", May 17, 2010, https://saravananthirumuruganathan.wordpress.com/2010/05/17/a-detailed-introduction-to-k-nearest-neighbor-knn-algorithm/, access: 15.08.2015

\bibitem{duda-hart-classification}
Richard O. Duda, Peter E. Hart, David G. Stork, "Pattern Classification, 2nd Edition", ISBN: 978-0-471-05669-0, November 2000

\bibitem{k_means}
Michael Steinbach, George Karypis, Vipin Kumar, "A Comparison of Document Clustering Techniques", Department of Computer Science and Egineering,  University of Minnesota, Technical Report \#00-034 

\bibitem{roc-curve}
https://docs.eyesopen.com/toolkits/cookbook/python/plotting/roc.html, access: 01.09.2015

\end{thebibliography}